---
title: "Homework 5"
author: "Mufeng Xu"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: github_document

---

```{r setup, include = FALSE}
library(tidyverse)
library(ggplot2)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Problem 1

Read in the data.

```{r}
homicide_df = 
  read_csv("./data/homicide_data/homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved",
    )
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL")
```

Let's look at this a bit

```{r}
aggregate_df = 
  homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    hom_total = n(),
    hom_unsolved = sum(resolved == "unsolved")
  )
```

Can I do a prop test for a single city?

```{r}
prop.test(
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_unsolved), 
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_total)) %>% 
  broom::tidy()
```

Try to iterate ........

```{r}
# map2 has 2 variables available for mapping
results_df = 
  aggregate_df %>% 
  mutate(
    prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x = .x, n = .y)),
    tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
  ) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_tests) %>% 
  select(city_state, estimate, conf.low, conf.high)
```

Make a plot

```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```


## Problem 2

import one dataset 

```{r}
lda_df = 
  tibble(
    path = list.files("data/lda_data")
  ) %>% 
  mutate(
    path = str_c("data/lda_data/", path),
    data = map(.x = path, ~read_csv(.x))
  ) %>% 
  unnest(data) %>% 
  separate(
    path,
    into = c("path_prefix1", "path_prefix2", "path_prefix3", "arm", "id", "csv"),
    sep = "([//_.])"
  ) %>% 
  select(
    -path_prefix1, -path_prefix2, -path_prefix3, -csv
    ) %>% 
  mutate(
    arm = case_when(
      arm == "con" ~ "control",
      arm == "exp" ~ "experimental"
    ),
    id = as.double(id)
  ) %>% 
  pivot_longer(
    week_1:week_8,
    names_prefix = "week_",
    names_to = "week",
    values_to = "observation"
  )
```


```{r}
lda_df %>% 
  mutate(
    arm_id = str_c(arm, "arm", id, sep = "_")
  ) %>% 
  ggplot(aes(x = week, y = observation, group = arm_id, color = arm)) +
  geom_line() +
  geom_point(size = 1) +
  theme_bw() +
  labs(
    title = "Spaghetti Plot of Observations on Each Subject over Time",
    x = "Week",
    y = "Observation Value"
    )
```

According to the spaghetti plot above, it can be observed that observation values of experimental arm are generally higher than those of control arm; observation values of experimental arm increases faster than those of control arm for the first some weeks; control values are more stable than experimental values; from week 7, all observation values for the experimental arm are higher than those of the control arm.










